(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-10 ms.tex
blah
tdm edits
fpp table changes

\newcommand{\Nfp}{4}
\newcommand{\Nvalidated}{21}
\newcommand{\Nlimbo}{11}

@@

\citet{Morton12} presented an automated method to calculate the
probability that a planet candidate might be caused by an
astrophysical false positive.
This method uses population simulations
of false positive scenarios and true transiting planets to quantify
the typical shape of each, comparing to the observed transit shape.
It then combines this information with observationally motivated prior
assumtions about the populations of field stars, the properties of
multiple star systems, and the occurrence rate of planets as determined
from \kep\ \citet{Fressin13}, in order to determine the probability that
the observed signal may be a false positive.
Similar in spirit to other published methods of
probabilistic validation, such as Blender \citep{} and PASTIS
\citep{}, it has the advantage of being computationally less demanding
and fully automated, and thus easily applied in batch to a large
number of candidates.

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new implementation of the \citet{Morton12} procedure, to calculate
false positive probabilities (FPPs) for each of these K2 candidates.
While we have obtained follow-up observations of a number of these systems,
we do the preliminary FPP calculations without taking these into account,
in order to demonstrate the power of \texttt{vespa} analysis
even in the absence of follow-up observations.
The constraints we impose on false positive scenarios in these
``follow-up free'' calculations are the following:
\begin{itemize}
\item A chance-aligned eclipsing binary system must reside within
a 4 arcsecond radius of the target star.
\item The maximum allowed depth of a potential secondary eclipse event,
determined as the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out.
\end{itemize}

@@

We emphasize that t

@@

EPIC 201555883 was originally listed in \paperit\ as a planet candidate.
After submission of that work, this object of interest was identified as
having a transit ephemeris consistent with that of EPIC 201569483,
which we identify as a likely eclipsing binary due to the observed transit
depth \anytodo{Right? Right?}.
We conclude the observed transit signal from EPIC 201555883 is likely the result
of an instrumental artifact.

@@

\include{table_photometry}

@@

%\include{table_fpp}

>>>>

\newcommand{\Nfp}{4}
\newcommand{\Nvalidated}{22}
\newcommand{\Nlimbo}{10} %adds to 36?  good.

@@

\citet{Morton12} presented an automated method to calculate the
probability that a planet candidate might be caused by an
astrophysical false positive.
This method uses population simulations of the light curves of
of false positive scenarios and true transiting planets to quantify
the typical shape of each, comparing to the observed transit shape.
It then combines this information with observationally motivated prior
assumptions about the populations of field stars, the properties of
multiple star systems, and the occurrence rate of planets as determined
from \kep\ \citet{Fressin13}, in order to determine the probability that
the observed signal may be a false positive.
Similar in spirit to other published methods of
probabilistic validation, such as Blender \citep{} and PASTIS
\citep{}, it has the advantage of being computationally less demanding
and fully automated, and thus easily applied in batch to a large
number of candidates.

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new general-purpose implementation of the \citet{Morton12} procedure, 
to calculate false positive probabilities (FPPs) for each of these 
K2 candidates.  We impose the following constraints on false positive
scenarios:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside within
a sky area equivalent to 8 arcsecond radius of the target star.
\item The maximum allowed depth of a potential secondary eclipse event,
determined as the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out.
\item High-resolution imaging constraints, where available (see below)
\end{itemize}

@@

We emphasize that the majority of these planets were validated based 
solely on the transit signal, with no need for follow-up imaging.  This
demonstrates the utility of \texttt{vespa} analysis, which will be
crucial to interpreting future \kt\ detected candidates and prioritizing
follow-up observing efforts.

@@

EPIC 201555883 was originally listed in \paperit\ as a planet candidate.
After submission of that work, this object of interest was identified as
having a transit ephemeris consistent with that of EPIC 201569483,
which we identify as a likely eclipsing binary due to the observed transit
depth \anytodo{Right? Right?  Can this be more quantitative?  Are these two stars 
close to one another?  How bright is  the purported parent? Are they 
On/near the same CCD column?  FPP gives this a pass, so we 
need to be clear about this.}.
We conclude the observed transit signal from EPIC 201555883 is likely the result
of an instrumental artifact.

@@

\include{table_photometry}
\turnpage

@@

\include{table_fpp}
